---
title: "District_Secession_memo"
author: "E Johnson"
date: "8/13/2019"
output: 
  pdf_document:
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(data.table)
library(knitr)
library(xtable)
suppressPackageStartupMessages(library(lubridate))
dt <- readRDS('~/Dropbox/pkg.data/nclb_segregation/Clean/district_secession_stats.rds')
source('R/get_secessions.R')
secessions <- get_secessions()

```

# Overview

This memo illustrates the dynamics of racial segregation and new school openings for each of the
`r length(unique(secessions[secession_status=='Seceded']$seceded_from_district_ncesid))` school districts which experienced a secession from `r min(secessions[!is.na(secession_year)]$secession_year)` through `r max(secessions[!is.na(secession_year)]$secession_year)`. There are four sections to the analysis. First, we discuss the data. Second, we perfrom a per district case study. Third, we present aggregate data. Finally, we illustrate some of the pitfalls and concerns with aggregation.

# Data

Data consists of school district secessions and school level demograhpic characteristics.

## Secession data

Secession data comes from EdBuild. A full discription of EdBuild's mission, funding, and members can be found at \url{https://edbuild.org}. The description of the data collection and analysis may be found at \url{https://edbuild.org/content/fractured/methodology}.

Edbuild identifies `r nrow(secessions[secession_status=='Seceded'])` successful secessions out of `r nrow(secessions)` attempts in United States school districts since `r min(secessions[!is.na(secession_year)]$secession_year)`. The number of successful sessions by year is shown in Figure \ref{fig:years}. Table \ref{tbl:secessionStatsState} shows the number of successful secessions by state.

```{r echo=FALSE, fig.width=4, fig.height=3, fig.cap="\\label{fig:years}Number of Successful Sessions by Year"}
annual_secessions <- secessions[, .(n_secessions = .N), by=secession_year][!is.na(secession_year)][order(-secession_year)]
#print(xtable(annual_secessions[order(as.integer(secession_year)), .(Year = as.character(secession_year), Count=n_secessions)],
#caption = "Successful Secessions by Year", label='tbl:secessionStatsYear'),
#      comment=FALSE,
#      include.rownames=FALSE)
ggplot2::ggplot(annual_secessions, aes(x=secession_year, y=n_secessions)) + geom_col() + theme_bw() + xlab('Year') + ylab('Number of Secessions')
```

```{r echo=FALSE, results='asis'}
state_secessions <- secessions[secession_status=='Seceded', .(n_secessions = .N), by=state_name][order(-n_secessions)]
print(xtable(state_secessions[order(as.integer(-n_secessions)), .(State = state_name, Count=n_secessions)],
caption = "Successful Secessions by State", label='tbl:secessionStatsState'),
      comment=FALSE,
      include.rownames=FALSE)
#ggplot2::ggplot(state_secessions, aes(x=state_name, y=n_secessions)) + geom_col() + theme_bw() + xlab('Year') + ylab('Number of Secessions')
```

\clearpage

# Individual Districts

Next, we examine individual districts.

```{r echo=FALSE, results='asis'}

```